Model

### 2019-04-16 stats/model.Rmd
first pass model inferring semantic strength

---
title: "Model"
author: "M. Bohn"
date: "12 4 2019"
output: html_document
---

@@

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
```

@@

var LexiconPrior = Categorical({vs: ["novel_word = novel_object","novel_word = familiar_object" ], ps: [1, 1]})
'
```

@@

@@

var speakerOptimality = 1;

@@

```{r}
webppl(program_code = paste(rsaUtils, rsaModel, sep='\n'))
```
# Model for ME Effect
```{r}
me_data <- read_csv("../data/child_basic_me.csv")%>%
    filter(trial != "train1",
           trial != "train2")%>%
  mutate(z_age = age_num - mean(age_num))

>>>>

---
title: "Model"
author: "M. Bohn"
output: html_document
---

@@

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

@@

var LexiconPrior = Categorical({vs: ["novel_word = novel_object","novel_word = familiar_object" ], ps: [1, 1]})

var foreach = function(fn, lst) {
    var foreach_ = function(i) {
        if (i < lst.length) {
            fn(lst[i]);
            foreach_(i + 1);
        }
    };
    foreach_(0);
};

var logistic = function(x) {1 / (1 + Math.exp(-x))}

var levels = function(df, label){
  return _.uniq(_.map(df, label));
}
'
```

@@

```{r}
baseMeModel <- '

@@

var speakerOptimality = 1

@@

```{r}
webppl(program_code = paste(rsaUtils, rsaModel, baseMeModel,sep='\n'))
```

# Inferring semantic knowledge
```{r}
semStr <- '
var data = dataFromR.data

var familiars = levels(data, "familiar")

var model  = function(){

  var params = map(function(cndtn){

    var conditionData = _.filter(data, {condition: cndtn})

    var sem_slope = uniformDrift({a: -5, b: 5, width: 0.2})
    var sem_int = uniformDrift({a: 0, b: 5, width: 0.2})

    foreach(function(row){

      var age = row.age

      var sem_knowledge = logistic(sem_int + sem_slope * age)

      observe(modelPredictions, row.correct)

    }, conditionData)

    return extend([
      {int: sem_int, slope: sem_slope, familiar: cndtn}
    ])

  }, familiars)

params

}
'
```

```{r}
me_model_data <- read_csv("../data/child_basic_me.csv")%>%
    filter(trial != "train1",
           trial != "train2")%>%
  mutate(age = age_num - min(age_num))

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 5000, burn = 2000, verbose = T)
)

sem_know <- sem_know_model %>%
  select(value) %>%
  map_df(bind_rows)%>%
  rename(int = `0.int`,
         slope = `0.slope`,
         familiar = `0.familiar`)%>% 
  gather(parameter, value, -familiar)

sem_know_params <- sem_know %>%
  group_by(familiar,parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))
```

```{r}
ggplot(sem_know, aes(value))+
  geom_density()+
  xlab("Parameter")+
  facet_grid(parameter ~familiar)+
  theme_few()
```
## Plotting semantic knowledge
```{r}

aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)

aoa_ratings <- aoa_ratings_all %>%
  filter(Word %in% sem_know_params$familiar )%>%
  mutate(mean_aoa = as.numeric(Rating.Mean),
         familiar = Word)%>%
  select(familiar,mean_aoa)

plot_sem_know <- sem_know_params%>%
  select(-uci,-lci)%>%
  spread(parameter, -familiar)%>%
  expand(familiar, slope, int,age = me_model_data$age)%>%
  mutate(sem_know = plogis(int + slope * age))%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))

ggplot(plot_sem_know, aes(x = age+2, y= sem_know, col = familiar))+
  geom_line(size = 1)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()+
  scale_colour_viridis_d(name = "familiar object")
```

# Ignore: Model for ME Effect
```{r}
me_data <- read_csv("../data/child_basic_me.csv")%>%
    filter(trial != "train1",
           trial != "train2")%>%
  mutate(z_age = age_num - mean(age_num))
